---
title: Books with Bookdown
author: Agustin Calatroni
date: '2018-02-12'
slug: books-with-bookdown
categories:
  - R
tags:
  - bookdown
  - books
---

There is a large amount of free resource available to learn R. Once such resource is the books created by authors using the [bookdown](https://bookdown.org/yihui/bookdown/) by Yihui Xie package. The bookdown package is built on top of R Markdown. Below I have created a table with those references that I had or plan to read. They go from a fantastic introduction to `ggplot2` or data science to more technical in nature as the Advance R by Hadley Wickham. As I discoved more resources I will be updating the table. Happy learning.

```{r include=FALSE}
library(tidyverse)
library(DT)
```

```{r include=FALSE}
bookdown <- tribble(
  ~Title, ~Author,  ~Link,
  
  "R for Data Science",
  "Garrett Grolemund and Hadley Wickham",
  "http://r4ds.had.co.nz",
    
  "Mastering Software Development in R",
  "Roger D. Peng, Sean Kross, and Brooke Anderson",
  "https://bookdown.org/rdpeng/RProgDA/",

  "YaRrr! The Pirate’s Guide to R",
  "Nathaniel D. Phillips",
  "https://bookdown.org/ndphillips/YaRrr/",
    
  "The Unix Workbench", 
  "Sean Kross", 
  "https://bookdown.org/sean/the-unix-workbench/",
  
  "Advanced R", 
  "Hadley Wickham", 
  "https://adv-r.hadley.nz/",
    
  "Technical Foundations of Informatics",
  "Michael Freeman and Joel Ross",
  "https://info201.github.io/",
  
  "Circular Visualization in R", 
  "Zuguang Gu", 
  "http://zuguang.de/circlize_book/book/",
  
  "Data Visualization A practical introduction",
  "Kieran Healy",
  "http://socviz.co/",
  
  "Introduction à R et au tidyverse",
  "Julien Barnier",
  "https://juba.github.io/tidyverse/",
    
  "plotly for R",
  "Carson Sievert",
  "https://plotly-book.cpsievert.me/",
    
  "Interpretable Machine Learning",
  "Christoph Molnar",
  "https://christophm.github.io/interpretable-ml-book/"
    
)
```

```{r echo=FALSE}
bookdown %>% 
  arrange(Title) %>% 
  datatable(filter = 'top',
            rownames = FALSE,
            options = list(pageLength = 15)
  )
```